### 2021-02-22 results.tex
add new results version

\rb{This is a nice place to present some details about the malwares
  that FlowDroid had detected, showin the additional source-sink pairs
  that emmerged. A discussion about these aforementioned four pairs would
  also be relevant.}

\rb{I finished my first review until this place. Tomorrow I will continue
from here.}

>>>>

Here we present details about one of the malwares that Flowdroid had detected. At this example, the malicious and benign apps have the same sink, however they access different sources, therefore configuring additional source-sink pairs, and hence a possible malicious behaviours. The pictures \ref{fig:sourcesink}, presents the paths source (blue border) and sink (orange border) from benign and malicious apps.

\begin{figure}[h]%
    \centering
    \subfloat[\centering Path source/sink from benign app]{{\includegraphics[width=5cm]{images/pathbenign.png} }}%
    \qquad
    \subfloat[\centering Path source/sink from malicious app]{{\includegraphics[width=5cm]{images/pathmalicious.png} }}%
    \caption{Pairs source/sink different (B/M)}%
    \label{fig:sourcesink}%
\end{figure}
